\thispagestyle{empty}

\paragraph{Instruction:} 

    \begin{enumerate}
        \item You must use the \LaTeX ~template: 
        \url{https://www.overleaf.com/read/qqntsyfqwwdb}. Make a copy of the template, and you can edit it. \href{https://www.overleaf.com}{Overleaf} is the recommended platform.  
            \begin{itemize} 
                \item The template includes further guidance on the content of the report. A snapshot of the report template is included here. 
                \item Important: Remove all instructions and placeholder text before you submit your final report.
                \item Ask questions on Campuswire for clarification.
            \end{itemize}
        
        \item There is a \textit{preliminary} report due on \textbf{November 16, 2025}:
            \begin{itemize}
                \item At a minimum, you must report what is working and what is not working with your compiler before going to the evaluation session.
                \item As a preliminary report, you should not spend a lot of time on this. If you are short on time, focus on coding and finishing the requirements.
            \end{itemize}
        \item The \textit{final} report is due with your compiler's code on \textbf{December 7, 2025}:
            \begin{itemize}
                \item All Sections are required.
                \item We expect the "Update after Evaluation" Section.
                \item The report is mandatory. If you do not submit this, we will penalize you heavily (up to half of the credit).
                \item A reminder that \textbf{no late submission is allowed} for both the report and the code.
            \end{itemize}
    \end{enumerate}

\clearpage